Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
data writing (1)

Original dataset is collected through US GSS, which is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States. Usually, it is conducted in person, however because of pandemic, it was conducted via online. Among numerous interesting findings from the dataset, we choose to analyze the 2016 United States presidential election. However, choosing specific variables related to the election was not easy since deciding who to vote is followed by countless factors.After looking over the variables, we chose age,race,gender,degree,born US, Family income, national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration as potential variables. 
We mainly divided the variables into two parts: personal information and thoughts on national policy. Age, race, gender, degree, born US and family income are respondents' personal information, and national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration are personal thoughts on national policy.

>>>>

Original dataset is collected through US GSS, which is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States. Usually, it is conducted in person, however because of pandemic, it was conducted via online. Among numerous interesting findings from the dataset, we choose to analyze the 2016 United States presidential election. This slightly deviates the US GSS goal, but we thought it clearly represents current situation of US. However, choosing specific variables related to the election was not easy since deciding who to vote is followed by countless factors.After looking over the variables, we chose age,race,gender,degree,born US, Family income, national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration as potential variables. 
We mainly divided the variables into two parts: personal information (Age, race, gender, degree, born US and family income) and thoughts on national policies (national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration).
As I mentioned above, deciding who to vote is followed by very complex system of thoughts. Thus, as we cut down the variables, they do not guarantee 100% of the vote.
